Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Updated text describing result graphs

The sum of the times it took for the underlying hash library to calculate the
hash operations are exhibited in Figures \ref{fig:graph:10001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{time spent hashing}.

The numbers for uploading and downloading of one 1GB file are summarized in
Tables \ref{tbl:hashingtimes:put1gb} and \ref{tbl:hashingtimes:get1gb}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof10001Bfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof10001Bfiles.pdf}
    \caption{Figures for hash operations of 1000 1B files.}
    \label{fig:graph:10001b}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof1001KBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof1001KBfiles.pdf}
    \caption{Figures for hash operations of 100 1KB files.}
    \label{fig:graph:1001kb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof501MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof501MBfiles.pdf}
    \caption{Figures for hash operations of 50 1MB files.}
    \label{fig:graph:501mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof5100MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof5100MBfiles.pdf}
    \caption{Figures for hash operations of five 100MB files.}
    \label{fig:graph:5100mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof11GBfile.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof11GBfile.pdf}
    \caption{Figures for hash operations of one 1GB file.}
    \label{fig:graph:11gb}
\end{figure}

>>>>

The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:10001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{time spent hashing}.

The numbers for uploading and downloading the 1GB file are summarized in
Tables \ref{tbl:hashingtimes:put1gb} and \ref{tbl:hashingtimes:get1gb}.
BLAKE, \ac{BMW}, Shabal and Simd outperforms \ac{SHA}-256 when both uploading
and downloading a 1GB file. The difference between the slowest (JH) and the
fastest (BLAKE) algorithm is 229.92s when uploading the one gigabyte file.

The third column in Tables \ref{tbl:hashingtimes:put1gb} and
\ref{tbl:hashingtimes:get1gb} contains the time spent doing other operations
than hashing, i.e. $Total time - Time spent hashing$. This number varies
between 227.37s and 252.66s during upload and 205.94s and 225.03s during
download.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading10001Bfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading10001Bfiles.pdf}
    \caption{Figures for hash operations of 1000 1B files.}
    \label{fig:graph:10001b}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading1001KBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading1001KBfiles.pdf}
    \caption{Figures for hash operations of 100 1KB files.}
    \label{fig:graph:1001kb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading501MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading501MBfiles.pdf}
    \caption{Figures for hash operations of 50 1MB files.}
    \label{fig:graph:501mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading5100MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading5100MBfiles.pdf}
    \caption{Figures for hash operations of five 100MB files.}
    \label{fig:graph:5100mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashinguploading11GBfile.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/Timespenthashingdownloading11GBfile.pdf}
    \caption{Figures for hash operations of one 1GB file.}
    \label{fig:graph:11gb}
\end{figure}
